---
title: '`hosmap` Codebook'
output: 
  html_document:
    toc: true # table of content true
    toc_float: true
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: true  ## if you want number sections at each table header
    theme: readable  # many options for theme, this one is my favorite.
    highlight: tango  # specifies the syntax highlighting style
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE)
```

```{r load data, results='hide',echo=FALSE}
les_packages = lapply(c("ade4","caret","tidyverse","ggthemes","DT","data.table","dplyr",
                        "readxl","rvest"),require, character.only = TRUE)
Sys.setlocale("LC_CTYPE", "thai")
options(encoding="UTF-8")

clean_var = function(var_names){
  v = gsub('[^a-zA-Z0-9]','',var_names)
  v = gsub(' ','_',var_names)
  return(tolower(v))
}

## load files
data_path = '../data/'
raw_path = '../data/raw/'
hospital_latlon = fread(paste0(data_path,'hospital_latlon.csv'), encoding = 'UTF-8',
                        data.table = FALSE)
accident_festival = fread(paste0(data_path,'accident_festival.csv'), encoding = 'UTF-8',
                        data.table = FALSE)
moph_hospital = fread(paste0(data_path,'moph_hospital.csv'), encoding = 'UTF-8',
                        data.table = FALSE)
```

This codebook details all data cleaning and transformations as well as their rationales for the `hosmap` project. Raw datasets are obtained via the open data initiative [Data.go.th](https://data.go.th) among other sources. Resulting datasets we use for our analysis are:

# Hospital Latitude/Longitude Data

`hospital_latlon.csv` contains `r dim(hospital_latlon)[1]` hospitals as listed by [Ministry of Public Health](http://203.157.10.8/hcode_2014/p_export.php?p=3) (downloaded as `hospital_addresses.csv`). We augmented the data with latitude and longitude of each hospital queried via [Google Map API](https://cloud.google.com/maps-platform/). Code can be found in `scripts/scrape_geocode.py`.

# MoPH-affiliated Hospital Data

`moph_hospital.csv` contains `r dim(moph_hospital)[1]` hospitals affiliated with MoPH as extracted from the pdf provided by [Collaborative Project to Increase Production of Rurual Doctor](http://www.cpird.in.th/index.php/news_activity/news-info/172-data-phdb-hos-2560.html) (downloaded as `moph_hospital.pdf`).

```{r}
#additional data for big hospitals
moph_hospital = fread(paste0(raw_path,'moph_hospital.csv'),
                        data.table = FALSE)
#choose only number columns
moph_hospital = moph_hospital[,c(3,6:dim(moph_hospital)[2])]
names(moph_hospital)[1] = 'hospital_code'
names(moph_hospital) = clean_var(names(moph_hospital))
write.csv(moph_hospital,paste0(data_path,'moph_hospital.csv'),row.names = FALSE)
```

# New Year Accident Data

`accident_festival.csv` contains `r dim(accident_festival)[1]` cases of accidents from the dataset provided by [National Institute for Emergency Medicine](https://data.go.th/DatasetDetail.aspx?id=7d61f508-d2e1-4f0c-8408-dfde29f111f5) (downloaded as `51-58_CutName_NewYear_Edit.xlsx`).


```{r}
accident_festival = read_excel(paste0(raw_path,'51-58_CutName_NewYear_Edit.xlsx'))
names(accident_festival) = c('year', 'iso', 'province','hospital_code', 'hospital_name', 'date', 'time', 'sex', 'age', 'location', 'patient_status', 'vehicle_1', 'vehicle_2', 'belt', 'drinking', 'reporter', 'referral_flag', 'result', 'days')
num_cols = c('year','date','age','days')
accident_festival$year = sapply(accident_festival$year,
  function(x) {
  as.numeric(paste0('25',strsplit(x,' ')[[1]][2])) - 543
  })
accident_festival[,num_cols] = apply(accident_festival[,num_cols],2,as.numeric)
write.csv(accident_festival,paste0(data_path,'accident_festival.csv'),row.names = FALSE)
```

# Nearest Hospital Fishnet

```{r}
nearest_hos = fread(paste0(raw_path,'nearest_hos.csv'),data.table = FALSE)
```

We did preprocessing with ArcGIS to cast a one-sq-km-tile fishnet over all of Thailand. This resulted in `r dim(nearest_hos)[1]` points. We then calculate the nearest Euclidean distance between each point with the nearest hospital. After that, we use [GraphHopper API](https://graphhopper.com/api/1/docs/routing) to find time and distance taken between those points (See `graphhopper_api.py`). The processed file is saved as `route_hos_all.csv`.
